Machine Learning Methods for Site-specific Input Management

### 2022-04-19 Codes/PrepareResults.rmd
large updates for 3rd round submission

```{r packages, cache = FALSE, include = FALSE}
# === packages ===#
# --- data wrangling--- #
library(sf)
library(data.table)
library(tidyverse)

@@

# Read the data

@@

# Illustrative yield response curve

+ show to *which degree N affects yield* (yield response to N) 
+ show how the relation between yield estimation error and the effect of N on yield increase is ()

## MB yield response to N
+ for comment 8
+ The figure illustrates how yield responds to N

@@

# --- MB function to N --- #
vis_MB_curve <-
  ggplot(res_y_dt[variable == "Yield"]) +
  geom_line(
    aes(x = N, y = value, group = factor(group))
  ) +
  # geom_point(data = sub_dt, aes(x = opt_N, y = value, alpha = "Yield at EONR"), color = "red", size = 1.5) +
  # geom_segment(data = sub_dt, aes(x = N, xend=N, y = value, yend=-Inf), linetype = "dashed") +
  scale_alpha_manual(
    name = NULL,
    values = 1,
    breaks = "Yield at EONR",
    guide = guide_legend(override.aes = list(
      linetype = 0,
      shape = 16,
      color = "red"
    ))
  ) +
  labs(y = "Yield (kg/ha)") +
  labs(x = "N (kg/ha)") +
  theme_dist
```

## MB yield response and estimated yield response by BRF
+ As a response to comment 6
+ The figure shows the true yield response function and predicted yields at five N experiment by BRF

```{r prepare-data-vis, cache = TRUE}
# /*===========================================*/
#' =  Prepare illustrative yield response curve estimated by RF =
# /*===========================================*/

# /*--------------------------------*/
#' ## Preparation
# /*--------------------------------*/
# --- ML functions --- #
library(grf)
source(here("GitControlled/Codes/0_2_functions_main_sim.R"))

@@

# subplots_infiled <- test_subplot_dt[,unique_subplot_id] %>% unique()

# cnn_pred <- 
#   here("Shared/Results/CNN_rawRes_onEval/alldata_model4.csv") %>%
#   fread() %>%
#   .[, c("subplot_id", "strip_id") := tstrsplit(id, "_", fixed=TRUE)] %>%
#   .[,unique_subplot_id := paste0(strip_id,"_",subplot_id)] %>%
#   .[sim==x & unique_subplot_id %in% subplots_infiled,] %>%
#   .[,.(sim, unique_subplot_id, rate, pred)] %>%
#   setnames(names(.), c("sim", "unique_subplot_id", "N", "CNN"))

@@

# /*===== Preparation for plots =====*/
# new one
# c("8_43", "2_20")
# old one
# c("2_18", "6_47")

vis_res_true <-
  res_true[unique_subplot_id %in% c("2_18", "6_47")]

@@

```{r make-plot-MB-BRF-y}
vis_MB_BRF_y <-
  ggplot() +
  # --- true yield response curve --- #
  geom_line(
    data = vis_res_true,
    aes(x = N, y = yield, group = unique_subplot_id)
  ) +
  geom_point(
    data = vis_all_points,
    aes(y = value, x = N, color = observed, shape = type),
    size = 2
  ) +
  geom_line(
    data = vis_all_points[type == "Predicted", ],
    aes(y = value, x = N, color = unique_subplot_id),
    linetype = 2,
    size = 0.5
  ) +
  geom_vline(
    xintercept = vis_res_true$aa_n %>% unique(),
    color = "red",
    linetype = 2,
    size = 0.3
  ) +
  # annotate(
  #   "text",
  #   x = 137,  y = 9700,
  #   label = "Observed Rate \n = 117 (kg/ha)",
  #   family = "Times",
  #   size = 2
  # ) +
  annotate(
    "text",
    x = 180, y = 9400,
    label = "Observed Rate \n = 150 (kg/ha)",
    family = "Times",
    size = 3
  ) +
  scale_shape_manual(
    values = c("Predicted" = 2, "True" = 16),
    name = "Yield Type"
  ) +
  scale_color_manual(
    values = c(
      "Observed Rate" = "red",
      "Unobserved Rate" = "blue"
    ),
    name = ""
  ) +
  facet_grid(. ~ model) +
  labs(y = "Yield (kg/ha)") +
  labs(x = "N (kg/ha)") +
  guides(color = "none") +
  theme_dist
```

# Variogram Prameter Table

@@

## Division of field: plots, subplots and cells (Visualization)

@@

# Distribution Map of Field Characteristics

## Experimental N design

@@

## Yield map

@@

## opt_N map

```{r, dependson = "setup"}

## Field Characteristics Map

@@

@@

# Results

## Source Results

@@

# Yield prediction results

## Report RMSE of of Yield Prediction (RF, BRF, CNN)

```{r, dependson = "source-results"}
# ==== Summary Table ====#
# --- on training data sets--- #
report_table_y_train <-
  res_y_train %>%
  .[, .(rmse_y = mean(rmse_y)), by = .(Method, Model)] %>%
  .[, rmse_y := format(round(rmse_y, 1), nsmall = 1)] %>%
  dcast(Model ~ Method, value.var = "rmse_y") %>%
  .[, CF_base := "-"] %>%
  mutate(
    across(
      everything(),
      as.character
    )
  ) %>%
  flextable(.) %>%
  set_header_labels(values = list(
    Model = "Model",
    RF = "RF",
    BRF = "BRF",
    CNN = "CNN",
    CF_base = "CF-base"
  )) %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  #- change the borders just for consistency with other figures -#
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  autofit()

# --- on testing data sets--- #
report_table_y <-
  res_y_test %>%
  .[, .(rmse_y = mean(rmse_y)), by = .(Method, Model)] %>%
  .[, rmse_y := format(round(rmse_y, 1), nsmall = 1)] %>%
  dcast(Model ~ Method, value.var = "rmse_y") %>%
  .[, CF_base := "-"] %>%
  mutate(
    across(
      everything(),
      as.character
    )
  ) %>%
  flextable(.) %>%
  set_header_labels(values = list(
    Model = "Model",
    RF = "RF",
    BRF = "BRF",
    CNN = "CNN",
    CF_base = "CF-base"
  )) %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  #- change the borders just for consistency with other figures -#
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  autofit()
```

## Figure (RMSE of EONR vs RMSE of yield for RF and BRF)

```{r}
# fig_y_optN <-
# res_y_test %>%
# .[Method %in% c("RF", "BRF", "CNN")] %>%
# ggplot(aes(x = rmse_y, y = rmse_optN)) +
# geom_point(size = 0.5) +
# facet_grid(Model ~ Method) +
# geom_smooth(method = "lm", se = FALSE, color = "red", size = 0.7) +
# stat_regline_equation(
#   label.x = 2050, label.y = 90,
#   aes(label = ..rr.label..),
#   size = 3
# ) +
# guides(
#   fill = guide_legend(keywidth = 1, keyheight = 1),
#   linetype = guide_legend(keywidth = 3, keyheight = 1),
#   colour = guide_legend(keywidth = 3, keyheight = 1)
# ) +
# ylim(NA, 95) +
# labs(y = " RMSE of EONR Estimation (kg/ha)") +
# labs(x = " RMSE of Yield Prediction (kg/ha)") +
# theme_dist
```

```{r}
# sim_no <- c(300, 600, 900)
sim_no <- c(10, 20, 30)

vis_RMSE_y_eonr <-
  res_y_test %>%
  .[sim %in% sim_no & Method %in% c("RF", "BRF", "CNN") & Model == "aabbyytt"] %>%
  ggplot() +
  geom_point(aes(x = rmse_y, y = rmse_optN, shape = Method, fill = factor(sim)), size = 2) +
  scale_shape_manual(values = c(21, 23, 25)) +
  ylim(NA, 95) +
  labs(y = " RMSE of EONR Estimation (kg/ha)") +
  labs(x = " RMSE of Yield Prediction (kg/ha)") +
  theme_dist +
  labs(fill = "Simulation Round", shape = "Method") +
  guides(fill = guide_legend(override.aes = list(shape = 21))) +
  # guides(fill=guide_legend(nrow=2, byrow=TRUE)) +
  # guides(shape=guide_legend(nrow=2, byrow=TRUE)) +
  theme(legend.position = "bottom", legend.box = "vertical", legend.margin = margin()) +
  labs(fill = "Simulation Round", shape = "Method")
```

## True Yields vs Predicted Yields by models
+ for comment 7
+ a figure plots true yields (without error, epsilon) against predicted yields by model (without CF of course) for a single simulation round with RMSE printed for each model.

@@

@@

# === Table creation === #
report_summary_res_CNN_RF_BRF <-
  summary_res_CNN_RF_BRF %>%
  flextable(.) %>%
  border_remove() %>%
  delete_part(part = "header") %>%
  add_header(
    Model = "Model",
    blank1 = "", count_y_RF = "RF", count_RF = "RF",
    blank2 = "", count_y_BRF = "BRF", count_BRF = "BRF",
    blank3 = "", count_y_CNN = "CNN", count_CNN = "CNN",
    blank4 = "", Total = "Total #YP",
    top = TRUE
  ) %>%
  merge_h(part = "header") %>%
  hline_bottom(j = c(3:4, 6:7, 9:10), part = "header") %>%
  add_header(
    Model = "",
    blank1 = "", count_y_RF = "#Y", count_RF = "#YP",
    blank2 = "", count_y_BRF = "#Y", count_BRF = "#YP",
    blank3 = "", count_y_CNN = "#Y", count_CNN = "#YP",
    blank4 = "", Total = "",
    top = FALSE
  ) %>%
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  footnote(
    value = as_paragraph("NOTE: #Y indicates the number of simulation rounds in which the model provided the lowest RMSE for yield prediction. #YP indicates the number of simulation rounds in which the model provided the lower RMSE of yield prediction and the highest profit at the same time."),
    ref_symbols = NA
  ) %>%
  # set_table_properties(width = .7, layout = "autofit") %>%
  fontsize(i = NULL, j = NULL, size = 9, part = "footer") %>%
  autofit() %>%
  width(j = c(3:4, 6:7, 9:10), width = 0.6) %>%
  width(j = 12, width = 0.82) %>%
  width(j = 1, width = 0.8) %>%
  width(j = c(2, 5, 8, 11), width = 0.1)
```

# EONR Estimation

@@

# /*----------------------------------*/
#' ## Summary Table
# /*----------------------------------*/
# === Preparation === #
table_optN_prep <-
  allML_summary_bySim %>%
  .[, .(
    rmse_optN = format(round(mean(rmse_optN), 1), nsmall = 1),
    pi_loss = format(round(mean(pi_loss), 2), nsmall = 2)
  ), by = .(type, Method, Model)] %>%
  dcast(type + Model ~ Method, value.var = c("rmse_optN", "pi_loss")) %>%
  .[, `:=`(
    blank1 = NA, blank2 = NA, blank3 = NA, blank4 = NA, blank5 = NA
  )] %>%
  .[, .(type, Model, blank1, rmse_optN_RF, pi_loss_RF, blank2, rmse_optN_BRF, pi_loss_BRF, blank3, rmse_optN_CNN, pi_loss_CNN, blank4, rmse_optN_CF_base, pi_loss_CF_base)]

@@

# === Summary Table (Testing Data sets) === #
report_table_optN <-
  table_optN_prep %>%
  .[type == "test", !"type"] %>%
  mutate(
    across(
      everything(),
      as.character
    )
  ) %>%
  # add_row(.after = 4) %>%
  flextable(.) %>%
  border_remove() %>%
  delete_part(part = "header") %>%
  add_header(
    Model = "Model",
    blank1 = "", rmse_optN_RF = "RF", pi_loss_RF = "RF",
    blank2 = "", rmse_optN_BRF = "BRF", pi_loss_BRF = "BRF",
    blank3 = "", rmse_optN_CNN = "CNN", pi_loss_CNN = "CNN",
    blank4 = "", rmse_optN_CF_base = "CF-base", pi_loss_CF_base = "CF-base",
    top = TRUE
  ) %>%
  merge_h(part = "header") %>%
  hline_bottom(j = c(3:4, 6:7, 9:10, 12:13), part = "header") %>%
  add_header(
    Model = "",
    blank1 = "", rmse_optN_RF = "RMSE", pi_loss_RF = "pi_loss",
    blank2 = "", rmse_optN_BRF = "RMSE", pi_loss_BRF = "pi_loss",
    blank3 = "", rmse_optN_CNN = "RMSE", pi_loss_CNN = "pi_loss",
    blank4 = "", rmse_optN_CF_base = "RMSE", pi_loss_CF_base = "pi_loss",
    top = FALSE
  ) %>%
  compose(i = 2, j = c(4, 7, 10, 13), part = "header", value = as_paragraph("\U1D70B\U0302", as_sub(as_i("def")))) %>%
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  # autofit() %>%
  # width(j = c(2,5,8,11), width=0.3) %>%
  # fix_border_issues()
  footnote(
    # i = 1, j = c(4, 7, 10, 13), part = "header",
    value = as_paragraph("NOTE: \U1D70B\U0302", as_sub(as_i("def")), " indicates profit-deficit ($/ha) relative to the true maximum profit at the subplot level. The maximized profit is the profit under the true yield response functions evaluated at ", as_i("\U004E\U2071"), as_sub(as_i("opt")), "."),
    ref_symbols = NA
  ) %>%
  fontsize(i = NULL, j = NULL, size = 9, part = "footer") %>%
  autofit() %>%
  width(j = c(3, 4, 6, 7, 9, 10, 12, 13), width = 0.6) %>%
  width(j = c(2, 5, 8, 11), width = 0.1)
```

# Profit Loss

## Profit loss summary and distributions
```{r}
piLoss_density <-
  allML_summary_bySim %>%
  .[type == "test", ] %>%
  .[Method == "CF_base", Method := "CF-base"] %>%
  .[, Model := case_when(
    Model == "aby" ~ "Scenario: aby",
    Model == "abytt" ~ "Scenario: abytt",
    Model == "aabbyy" ~ "Scenario: aabbyy",
    Model == "aabbyytt" ~ "Scenario: aabbyytt"
  )] %>%
  .[, Model := factor(Model,
    levels = c("Scenario: aby", "Scenario: abytt", "Scenario: aabbyy", "Scenario: aabbyytt")
  )] %>%
  ggplot() +
  geom_density(aes(x = pi_loss, fill = Method), alpha = 0.7) +
  labs(x = expression(paste(hat(pi)[italic("def")], " ($/ha)"))) +
  facet_wrap(~Model, ncol = 1) +
  theme_dist
```

# Treatment effect comparison

@@

# An Example of a Causal Tree

@@

# Various Error Size (Appendix)

## EONR Estimation

@@

## Yield Prediction

>>>>

```{r packages, cache = FALSE, include = FALSE}
# === packages ===#
library(here)
# --- data wrangling--- #
library(sf)
library(data.table)
library(tidyverse)

@@

# Read Field Data

@@

# Illustrative Examples of MB Yield Response Curves (Figure 2)

@@

# --- MB function to N --- #
vis_MB_curve <-
  ggplot(res_y_dt[variable == "Yield"]) +
  geom_line(
    aes(x = N, y = value, group = factor(group))
  ) +
  scale_alpha_manual(
    name = NULL,
    values = 1,
    breaks = "Yield at EONR",
    guide = guide_legend(override.aes = list(
      linetype = 0,
      shape = 16,
      color = "red"
    ))
  ) +
  labs(y = "Yield (kg/ha)") +
  labs(x = "N (kg/ha)") +
  theme_dist
```

# Illustrative Examples of Yield Response Curves Estimated by RF and BRF (Figure 7)

```{r prepare-data-vis, cache = TRUE}
# /*--------------------------------*/
#' ## Preparation
# /*--------------------------------*/
# --- ML functions --- #
library(grf)
source(here("GitControlled/Codes/0_2_functions_main_sim.R"))

@@

@@

# /*===== Preparation for plots =====*/
vis_res_true <-
  res_true[unique_subplot_id %in% c("2_18", "6_47")]

@@

```{r make-plot-MB-BRF-y}
vis_MB_BRF_y <-
  ggplot() +
  # --- true yield response curve --- #
  geom_line(
    data = vis_res_true,
    aes(x = N, y = yield, group = unique_subplot_id)
  ) +
  geom_point(
    data = vis_all_points,
    aes(y = value, x = N, color = observed, shape = type),
    size = 2
  ) +
  geom_line(
    data = vis_all_points[type == "Predicted", ],
    aes(y = value, x = N, color = unique_subplot_id),
    linetype = 2,
    size = 0.5
  ) +
  geom_vline(
    xintercept = vis_res_true$aa_n %>% unique(),
    color = "red",
    linetype = 2,
    size = 0.3
  ) +
  annotate(
    "text",
    x = 180, y = 9400,
    label = "Observed Rate \n = 150 (kg/ha)",
    family = "Times",
    size = 3
  ) +
  scale_shape_manual(
    values = c("Predicted" = 2, "True" = 16),
    name = "Yield Type"
  ) +
  scale_color_manual(
    values = c(
      "Observed Rate" = "red",
      "Unobserved Rate" = "blue"
    ),
    name = ""
  ) +
  facet_grid(. ~ model) +
  labs(y = "Yield (kg/ha)") +
  labs(x = "N (kg/ha)") +
  guides(color = "none") +
  theme_dist
```

@@

## Division of Field: plots, subplots and cells (Figure 1)

@@

## Experimental N Design (Figure 3 Left)

@@

## Yield Map (Figure 3 Right)

@@

## Field Characteristics Map (Appendix: Figure C.1)

@@

## Low and High Yield Error Maps (Appendix: Figure G.1)

@@

# Simulation Results

## Load the Results

@@

# Yield Prediction Results from the Main Simulations

## Summary Table for RMSE of of Yield Prediction

### on Training Datasets (Appendix: Table F.2)

```{r, dependson = "source-results"}
# /*===== On training datasets =====*/
report_table_y_train <-
  res_y_train %>%
  .[, .(rmse_y = mean(rmse_y)), by = .(Method, Model)] %>%
  .[, rmse_y := format(round(rmse_y, 1), nsmall = 1)] %>%
  dcast(Model ~ Method, value.var = "rmse_y") %>%
  .[, CF_base := "-"] %>%
  mutate(
    across(
      everything(),
      as.character
    )
  ) %>%
  flextable(.) %>%
  set_header_labels(values = list(
    Model = "Model",
    RF = "RF",
    BRF = "BRF",
    CNN = "CNN",
    CF_base = "CF-base"
  )) %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  #- change the borders just for consistency with other figures -#
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  autofit()
```

### on Testing Datasets (Table 2)

```{r, dependson = "source-results"}
# --- on testing data sets--- #
report_table_y <-
  res_y_test %>%
  .[, .(rmse_y = mean(rmse_y)), by = .(Method, Model)] %>%
  .[, rmse_y := format(round(rmse_y, 1), nsmall = 1)] %>%
  dcast(Model ~ Method, value.var = "rmse_y") %>%
  .[, CF_base := "-"] %>%
  mutate(
    across(
      everything(),
      as.character
    )
  ) %>%
  flextable(.) %>%
  set_header_labels(values = list(
    Model = "Model",
    RF = "RF",
    BRF = "BRF",
    CNN = "CNN",
    CF_base = "CF-base"
  )) %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  #- change the borders just for consistency with other figures -#
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  autofit()
```

## The Relationship between yield and EONR Prediction Performances under the aabbyytt scenario (Figure 8)

```{r}
sim_no <- c(10, 20, 30)

vis_RMSE_y_eonr <-
  res_y_test %>%
  .[sim %in% sim_no & Method %in% c("RF", "BRF", "CNN") & Model == "aabbyytt"] %>%
  ggplot() +
  geom_point(aes(x = rmse_y, y = rmse_optN, shape = Method, fill = factor(sim)), size = 2) +
  scale_shape_manual(values = c(21, 23, 25)) +
  ylim(NA, 95) +
  labs(y = " RMSE of EONR Estimation (kg/ha)") +
  labs(x = " RMSE of Yield Prediction (kg/ha)") +
  theme_dist +
  labs(fill = "Simulation Round", shape = "Method") +
  guides(fill = guide_legend(override.aes = list(shape = 21))) +
  theme(legend.position = "bottom", legend.box = "vertical", legend.margin = margin()) +
  labs(fill = "Simulation Round", shape = "Method")
```

## True Yields without Error vs Predicted Yields (Appendix: Figure E.1)

@@

## Yield Prediction vs EONR estimation : Count Table in terms of profit loss (Table 3)

@@

# === Table creation === #
report_summary_res_CNN_RF_BRF <-
  summary_res_CNN_RF_BRF %>%
  flextable(.) %>%
  border_remove() %>%
  delete_part(part = "header") %>%
  add_header(
    Model = "Model",
    blank1 = "", count_y_RF = "RF", count_RF = "RF",
    blank2 = "", count_y_BRF = "BRF", count_BRF = "BRF",
    blank3 = "", count_y_CNN = "CNN", count_CNN = "CNN",
    blank4 = "", Total = "Total #YP",
    top = TRUE
  ) %>%
  merge_h(part = "header") %>%
  hline_bottom(j = c(3:4, 6:7, 9:10), part = "header") %>%
  add_header(
    Model = "",
    blank1 = "", count_y_RF = "#Y", count_RF = "#YP",
    blank2 = "", count_y_BRF = "#Y", count_BRF = "#YP",
    blank3 = "", count_y_CNN = "#Y", count_CNN = "#YP",
    blank4 = "", Total = "",
    top = FALSE
  ) %>%
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  footnote(
    value = as_paragraph("NOTE: #Y indicates the number of simulation rounds in which the model provided the lowest RMSE for yield prediction. #YP indicates the number of simulation rounds in which the model provided the lower RMSE of yield prediction and the highest profit at the same time."),
    ref_symbols = NA
  ) %>%
  fontsize(i = NULL, j = NULL, size = 9, part = "footer") %>%
  autofit() %>%
  width(j = c(3:4, 6:7, 9:10), width = 0.6) %>%
  width(j = 12, width = 0.82) %>%
  width(j = 1, width = 0.8) %>%
  width(j = c(2, 5, 8, 11), width = 0.1)
```

# EONR Estimation from the Main Simulations

## Distributions of RMSE of EONR estimation over simulations (Figure 4)

@@

## Summary Table for RMSE of EONR estimation

### on Training Datasets (Appendix: Table F.1)

```{r, dependson = "source-results"}
# /*----------------------------------*/
#' ## Summary Table
# /*----------------------------------*/
# === Preparation === #
table_optN_prep <-
  allML_summary_bySim %>%
  .[, .(
    rmse_optN = format(round(mean(rmse_optN), 1), nsmall = 1),
    pi_loss = format(round(mean(pi_loss), 2), nsmall = 2)
  ), by = .(type, Method, Model)] %>%
  dcast(type + Model ~ Method, value.var = c("rmse_optN", "pi_loss")) %>%
  .[, `:=`(
    blank1 = NA, blank2 = NA, blank3 = NA, blank4 = NA, blank5 = NA
  )] %>%
  .[, .(type, Model, blank1, rmse_optN_RF, pi_loss_RF, blank2, rmse_optN_BRF, pi_loss_BRF, blank3, rmse_optN_CNN, pi_loss_CNN, blank4, rmse_optN_CF_base, pi_loss_CF_base)]

@@

### on Testing Datasets (Table 1)

```{r, dependson = "source-results"}
# === Summary Table (Testing Data sets) === #
report_table_optN <-
  table_optN_prep %>%
  .[type == "test", !"type"] %>%
  mutate(
    across(
      everything(),
      as.character
    )
  ) %>%
  # add_row(.after = 4) %>%
  flextable(.) %>%
  border_remove() %>%
  delete_part(part = "header") %>%
  add_header(
    Model = "Model",
    blank1 = "", rmse_optN_RF = "RF", pi_loss_RF = "RF",
    blank2 = "", rmse_optN_BRF = "BRF", pi_loss_BRF = "BRF",
    blank3 = "", rmse_optN_CNN = "CNN", pi_loss_CNN = "CNN",
    blank4 = "", rmse_optN_CF_base = "CF-base", pi_loss_CF_base = "CF-base",
    top = TRUE
  ) %>%
  merge_h(part = "header") %>%
  hline_bottom(j = c(3:4, 6:7, 9:10, 12:13), part = "header") %>%
  add_header(
    Model = "",
    blank1 = "", rmse_optN_RF = "RMSE", pi_loss_RF = "pi_loss",
    blank2 = "", rmse_optN_BRF = "RMSE", pi_loss_BRF = "pi_loss",
    blank3 = "", rmse_optN_CNN = "RMSE", pi_loss_CNN = "pi_loss",
    blank4 = "", rmse_optN_CF_base = "RMSE", pi_loss_CF_base = "pi_loss",
    top = FALSE
  ) %>%
  compose(i = 2, j = c(4, 7, 10, 13), part = "header", value = as_paragraph("\U1D70B\U0302", as_sub(as_i("def")))) %>%
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  # autofit() %>%
  # width(j = c(2,5,8,11), width=0.3) %>%
  # fix_border_issues()
  footnote(
    # i = 1, j = c(4, 7, 10, 13), part = "header",
    value = as_paragraph("NOTE: \U1D70B\U0302", as_sub(as_i("def")), " indicates profit-deficit ($/ha) relative to the true maximum profit at the subplot level. The maximized profit is the profit under the true yield response functions evaluated at ", as_i("\U004E\U2071"), as_sub(as_i("opt")), "."),
    ref_symbols = NA
  ) %>%
  fontsize(i = NULL, j = NULL, size = 9, part = "footer") %>%
  autofit() %>%
  width(j = c(3, 4, 6, 7, 9, 10, 12, 13), width = 0.6) %>%
  width(j = c(2, 5, 8, 11), width = 0.1)
```

## Distributions of profit deficit over simulations (Figure 5)

```{r}
piLoss_density <-
  allML_summary_bySim %>%
  .[type == "test", ] %>%
  .[Method == "CF_base", Method := "CF-base"] %>%
  .[, Model := case_when(
    Model == "aby" ~ "Scenario: aby",
    Model == "abytt" ~ "Scenario: abytt",
    Model == "aabbyy" ~ "Scenario: aabbyy",
    Model == "aabbyytt" ~ "Scenario: aabbyytt"
  )] %>%
  .[, Model := factor(Model,
    levels = c("Scenario: aby", "Scenario: abytt", "Scenario: aabbyy", "Scenario: aabbyytt")
  )] %>%
  ggplot() +
  geom_density(aes(x = pi_loss, fill = Method), alpha = 0.7) +
  labs(x = expression(paste(hat(pi)[italic("def")], " ($/ha)"))) +
  facet_wrap(~Model, ncol = 1) +
  theme_dist
```

## Treatment effect comparison (Figure 6)

@@

# Appendix

## Variogram Prameter Table (Appendix: Table C.1)

## An Example of a Causal Tree (Appendix: Figure A.1)

@@

## Various Error Size - EONR Estimation (Appendix: Table G.1)

@@

## Various Error Size - Yield Prediction (Appendix: Table G.2)
